251 MA

### 2023-03-07 code/process.Rmd
making images

```{r}
d_es_predInt |> 
  filter(target_d_calc < 5, rep_d_calc < 5) |>
  ggplot(aes(x=target_d_calc, y=rep_d_calc, color=sub_rep))+
  geom_point() +
  geom_abline(slope=1, intercept=0, lty = 2)+
  geom_smooth(method = "lm") + 
  geom_hline(yintercept = 0, lty = 2)+
  scale_color_viridis(discrete=F, direction = 1, 
                      name = "Subjective Replication Success")+
  labs(color="subrep", x="Original SMD", y="Replication SMD") + 
  theme(legend.position = "bottom")

@@

```{r}
tier1_subjective |> 
gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> 
  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting subjective replication score")+theme(axis.text=element_text(size=11))
```

@@

```{r}
tier2_predint |> 
gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> filter(Term!="Intercept") |> 
  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting replication in predictive interval")+theme(axis.text=element_text(size=11))
```

@@

```{r}
tier2_porig |> 
gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> filter(Term!="Intercept") |> 
  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting p_original")+theme(axis.text=element_text(size=11))
```
```{r, eval=T}
tier3_subjective <- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                          z_target_d_calc + z_log_p+ 
                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                             z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                             z_target_d_calc + z_log_p| academic_year),
                        family="cumulative",
                        data=data_tier3 |> mutate(sub_rep=sub_rep*4+1),
                        file=here(model_location, "tier3_subjective"),
                        prior=priors, 
                        control=list(adapt_delta=.99),
                        backend="cmdstanr")
```

```{r}
tier3_subjective |> 
gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> 
  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting subjective replication with stats predictors")+theme(axis.text=element_text(size=11))
```

@@

```{r}
tier3_predint |> 
gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> filter(Term!="Intercept") |> 
  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting predictive interval with stats predictors")+theme(axis.text=element_text(size=11))
```

@@

```{r}
tier3_porig |> 
gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> filter(Term!="Intercept") |> 
  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting p_original with stats predictors")+theme(axis.text=element_text(size=11))
```

@@

@@

@@

@@

ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==60), min.segment.length = 100, nudge_x = 20, na.rm = TRUE)+
    annotate("text", x=30, y=.15,label="Predicting p-original", color="black", size=5, hjust=1)+
theme(legend.position="none")+ scale_color_tableau("Classic 20")+
  coord_cartesian(xlim=c(0,90))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank(), legend.position="none")
```

@@

ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==55), min.segment.length = 100, nudge_x = 15, na.rm = TRUE)+
      annotate("text", x=30, y=1.3,label="Predicting predictive interval", color="black", size=5, hjust=1)+ 
theme(legend.position="none")+ scale_color_tableau("Classic 20")+
  coord_cartesian(xlim=c(0,80))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())

@@

@@

ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==60), min.segment.length = 100, nudge_x = 15, na.rm = TRUE)+ theme(legend.position="none")+ scale_color_tableau("Classic 20")+
      annotate("text", x=40, y=.25,label="Predicting predictive interval", color="black", size=5, hjust=1)+

@@

@@

@@

@@

@@

@@

@@

@@

ggplot(dat, aes(x=ifelse(single_vignette, "1 vignette", "multiple vignettes"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.title.x=element_blank())+theme( axis.text=element_text(size=11))
```

@@

@@

@@

@@

@@

>>>>

```{r}
d_es_predInt |> 
  filter(target_d_calc < 5, rep_d_calc < 5) |>
  ggplot(aes(x=target_d_calc, y=rep_d_calc, color=sub_rep))+
  geom_point() +
  geom_abline(slope=1, intercept=0, lty = 2)+
  geom_smooth(method = "lm") + 
  geom_hline(yintercept = 0, lty = 2)+
  scale_color_viridis(discrete=F, direction = 1, 
                      name = "Subjective\nReplication\nSuccess\n")+
  labs(color="subrep", x="Original SMD", y="Replication SMD") + 
  theme(legend.position = "right")

ggsave(here("plots/smd.pdf"))

@@

```{r}
tier1_subjective |> 
gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> 
  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting subjective replication score")+theme(axis.text=element_text(size=11))

ggsave(here("plots/tier1.pdf"))

@@

```{r}
tier2_predint |> 
gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> filter(Term!="Intercept") |> 
  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting replication in prediction interval")+theme(axis.text=element_text(size=11))

ggsave(here("plots/tier2_pred.pdf"))

@@

```{r}
tier2_porig |> 
gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> filter(Term!="Intercept") |> 
  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting p_original")+theme(axis.text=element_text(size=11))

ggsave(here("plots/porig.pdf"))

```
```{r, eval=T}
tier3_subjective <- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                          z_target_d_calc + z_log_p+ 
                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                             z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                             z_target_d_calc + z_log_p| academic_year),
                        family="cumulative",
                        data=data_tier3 |> mutate(sub_rep=sub_rep*4+1),
                        file=here(model_location, "tier3_subjective"),
                        prior=priors, 
                        control=list(adapt_delta=.99),
                        backend="cmdstanr")
```

```{r}
tier3_subjective |> 
gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> 
  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting subjective replication with stats predictors")+theme(axis.text=element_text(size=11))

ggsave(here("plots/tier3sub.pdf"))
```

@@

```{r}
tier3_predint |> 
gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> filter(Term!="Intercept") |> 
  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting prediction interval with stats predictors")+theme(axis.text=element_text(size=11))

ggsave(here("plots/tier3pred.pdf"))

@@

```{r}
tier3_porig |> 
gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> filter(Term!="Intercept") |> 
  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting p_original with stats predictors")+theme(axis.text=element_text(size=11))

ggsave(here("plots/tier3porig.pdf"))

@@

ggsave(here("plots/corr.pdf"))

@@

#corr_mat |> as_tibble(rownames="value2") |> pivot_longer(cols=!value2, names_to="value1", values_to = "corr") |> arrange(desc(corr)) |> filter(value2 <value1)
ggsave(here("plots/corr_all.pdf"))

@@

ggsave(here("plots/tier1_lasso.pdf"))

@@

ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==60), min.segment.length = 100, nudge_x = 20, na.rm = TRUE)+
    annotate("text", x=30, y=.15,label="Predicting p-original", color="black", size=5, hjust=1)+
theme(legend.position="none")+ scale_color_tableau("Classic 20")+
  coord_cartesian(xlim=c(0,90))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank(), legend.position="none")

ggsave(here("plots/tier2_lasso_porig.pdf"))

@@

ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==55), min.segment.length = 100, nudge_x = 15, na.rm = TRUE)+
      annotate("text", x=30, y=1.3,label="Predicting prediction interval", color="black", size=5, hjust=1)+ 
theme(legend.position="none")+ scale_color_tableau("Classic 20")+
  coord_cartesian(xlim=c(0,80))+theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.ticks.x=element_blank())

ggsave(here("plots/tier2_lasso_pred.pdf"))

@@

ggsave(here("plots/tier3_lasso_sub.pdf"))

@@

ggplot(to_plot, aes(x=time, y=value, color=var, label=var))+geom_line()+geom_label_repel(data=to_plot |> filter(time==60), min.segment.length = 100, nudge_x = 15, na.rm = TRUE)+ theme(legend.position="none")+ scale_color_tableau("Classic 20")+
      annotate("text", x=40, y=1.5,label="Predicting prediction interval", color="black", size=5, hjust=1)+

@@

ggsave(here("plots/tier3_lasso_pred.pdf"))

@@

ggsave(here("plots/tier3_lasso_porig.pdf"))

@@

ggsave(here("plots/score_all.pdf"))

@@

ggsave(here("plots/subfield.pdf"))

@@

ggsave(here("plots/openness.pdf"))

@@

 ggsave(here("plots/stanford.pdf"))

@@

ggsave(here("plots/modality.pdf"))

@@

ggsave(here("plots/within.pdf"))

ggplot(dat, aes(x=ifelse(single_vignette, "1 vignette", "multiple vignettes"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.title.x=element_blank())+theme( axis.text=element_text(size=11))

ggsave(here("plots/vignette.pdf"))

@@

ggsave(here("plots/pubyear.pdf"))

@@

ggsave(here("plots/ss_v_sample.pdf"))

@@

ggsave(here("plots/ss_ratio.pdf"))

ggplot(d_for_model, aes(x=log_trials, y=log_sample, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()+theme( axis.text=element_text(size=11))

ggsave(here("plots/sample_v_trials.pdf"))

ggplot(d_for_model, aes(x=log_trials+log_sample, y=sub_rep, color=sub_rep))+geom_jitter()+geom_smooth(method="lm")+scale_color_viridis()+theme( axis.text=element_text(size=11))+labs(x="Trials * Subjects (log scale)")

ggsave(here("plots/trial_sample.pdf"))

@@

ggsave(here("plots/log_sample.pdf"))

@@

ggsave(here("plots/log_trials.pdf"))
